Manuscript 1 code

### 2025-01-21 manuscript_1_code.Rmd
orgranized code and wrote new csvs for potential SEM

diversity_stability_synchrony <- left_join(diversity_stability, lm_synchrony, by = join_by(location))
diversity_stability_synchrony$synchrony_trans <- sv_trans(diversity_stability_synchrony$synchrony)

dss_ranges <- extract_ranges(diversity_stability_synchrony, "habitat",
                             c("richness_mean", "functional_richness_mean", "cover_stability", "synchrony"))

@@

### mean plot-level dss setup
```{r mean plot dss}
# calculate mean synchrony within a site (!= synchrony of species at the site level!)
mean_synchrony_stability <- diversity_stability_synchrony %>% 
  dplyr::group_by(habitat, site) %>% 
  dplyr::summarise(
    richness_mean = mean(richness_mean, na.rm = T),
    functional_richness_mean = mean(functional_richness_mean, na.rm = T),
    synchrony_mean = mean(synchrony, na.rm = T),
    stability_mean = mean(cover_stability, na.rm = T),
    cover_mean = mean(cover_mean, na.rm = T))
```
### synchrony and cover model

@@

# merge with site level dss metrics
dss_spatial <- merge(diversity_stability_site, spatial_synchrony, by = "site_habitat")
dss_spatial_2 <- merge(dss_spatial, mean_synchrony_stability, by = c("habitat", "site"))

dss_spatial_ranges <- extract_ranges(dss_spatial_2, "habitat", c("spatial_synchrony", "synchrony_mean", "stability_mean"))

>>>>

diversity_stability_synchrony <- left_join(diversity_stability, lm_synchrony, by = join_by(location))
diversity_stability_synchrony$synchrony_trans <- sv_trans(diversity_stability_synchrony$synchrony)
# write.csv(file = here::here("data", "full_plot_level_dss.csv"), diversity_stability_synchrony)

# calculate mean synchrony within a site (!= synchrony of species at the site level!)
mean_synchrony_stability <- diversity_stability_synchrony %>% 
  dplyr::group_by(habitat, site) %>% 
  dplyr::summarise(
    richness_mean = mean(richness_mean, na.rm = T),
    functional_richness_mean = mean(functional_richness_mean, na.rm = T),
    synchrony_mean = mean(synchrony, na.rm = T),
    stability_mean = mean(cover_stability, na.rm = T),
    cover_mean = mean(cover_mean, na.rm = T))

# write.csv(file = here::here("data", "mean_plot_level_dss.csv"), mean_synchrony_stability)
dss_ranges <- extract_ranges(diversity_stability_synchrony, "habitat",
                             c("richness_mean", "functional_richness_mean", "cover_stability", "synchrony"))

@@

### synchrony and cover model

@@

# merge with site level dss metrics
dss_spatial <- merge(diversity_stability_site, spatial_synchrony, by = "site_habitat")
dss_spatial_2 <- merge(dss_spatial, mean_synchrony_stability[, which(names(mean_synchrony_stability) %in%
                                                               c("habitat", "site", "synchrony_mean", "stability_mean"))],
                       by = c("habitat", "site"))
# write.csv(file = here::here("data", "spatial_synchrony.csv"), dss_spatial_2)
dss_spatial_ranges <- extract_ranges(dss_spatial_2, "habitat", c("spatial_synchrony", "synchrony_mean", "stability_mean"))
